Differnces-in-Differences with Spatial Spillover

### 2020-12-03 latex/slides/Spillover_slides.tex
Added slides for bias-adjustment and inference

\begin{frame}{Spatial Spillovers}
    Effects of treatments at states, counties, etc. can spill over boundaries.

    \begin{itemize}
        \item e.g. large employer opening/closing in a county have positive or negative employment effects on nearby counties
    \end{itemize}

    Differences-in-differences that compare outcomes among treated units with ``control'' units are biased from the spillover of effects.
\end{frame}

@@

@@

        \item Assume, for now, there is only spillover on the control.

@@

>>>>

\begin{frame}{Spatial Spillovers}

    Researchers use difference-in-differences to estimate the average treatment effect on the treated: 
    \[
        \mathbb{E} \{ Y_{i1}(1) - Y_{i1}(0) \ \vert \ D_{i} = 1 \}
    \]

    Effects of treatments at states, counties, etc. can spill over boundaries.

    \begin{itemize}
        \item e.g. large employer opening/closing in a county have positive or negative employment effects on nearby counties
    \end{itemize}
\end{frame}

\begin{frame}{Spatial Spillovers}
    The difference-in-differences estimate is: 
    \[ 
        \hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - 
        \hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]     
    \]

    Two problems in presence of spillover effects: 
    \begin{itemize}
        \item Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment

        \item Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
    \end{itemize}

@@

\begin{frame}{Partial Identification}
    Now, I turn to formalizing the above example following the literature on partial identification for treatment effects: \begin{citecolor}
        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
    \end{citecolor}

    In this framework, researchers need to specify bounds on spillovers in the context of their research question.
\end{frame}

\begin{frame}{Partially-identified Set}
    Following \citet{Rambachan_Roth_2020} and \citet{Manski_Pepper_2018}, researchers can provide bounds to the maximum spillovers.

    Let $\Delta$ denote the interval of potential biases: 
    \begin{align*}
        \Delta &\equiv [\underline{\Delta}, \overline{\Delta}] \\
        &= \left[ \min \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}, \ \max \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \right] 
    \end{align*}

    The partially identified set is formed by \[ 
        \left[\hat{\tau} - \underline{\Delta} , \ \hat{\tau} + \overline{\Delta} \right]    
    \]

\begin{frame}{Bias-adjusted Inference}

    Inference can be done following \citet{Rambachan_Roth_2020} by creating a Fixed-Length Confidence Interval: 
    \[ 
        \left[
            \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}
        \right]
    \]

    These standard errors should account for the spatial structure of outcomes following \citet{Conley_1999}.
\end{frame}

@@

        \item Assume, for now, there is only spillover on the control, i.e. $\tau_{\text{spillover,treat}} = 0$.

@@

% @kylebutts @TODO: show parametrization fixes biases.
